Chatbots in the classroom: a analysis from the teacher's perspective

### 2021-04-28 edubots_surveys.Rnw
Decided on title closes #4
Adds /me #8

\title{}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
% noteref={n1},                        % id's of article notes, if any
  email={jane.e.doe@cambridge.co.uk}   % email address
]{\inits{J.E.}\fnm{Jane E.} \snm{Doe}}
\author[
  addressref={aff1,aff2},
  email={john.RS.Smith@cambridge.co.uk}
]{\inits{J.R.S.}\fnm{John R.S.} \snm{Smith}}

@@

\address[id=aff1]{%                           % unique id
  \orgdiv{Department of Science},             % department, if any
  \orgname{University of Cambridge},          % university, etc
  \city{London},                              % city
  \cny{UK}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Institute of Biology},
  \orgname{National University of Sciences},
  %\street{},
  %\postcode{}
  \city{Kiel},
  \cny{Germany}
}

>>>>

\title{Chatbots in the classroom: a analysis from the teacher's perspective}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1,aff2},
  email={john.RS.Smith@cambridge.co.uk}
]{\inits{J.R.S.}\fnm{John R.S.} \snm{Smith}}

@@

\address[id=aff1]{%                           % unique id
  \orgdiv{Department of Computer Architecture and Technology},             % department, if any
  \orgname{University of Granada},          % university, etc
  \city{Granada},                              % city
  \cny{Spain}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Institute of Biology},
  \orgname{National University of Sciences},
  %\street{},
  %\postcode{}
  \city{Kiel},
  \cny{Germany}
}
